Supplementary Materials

### 2024-10-19 pilot-publication/supplementary-outcome-tables.Rmd
Compile new version of manuscript

## Table S2 Outcomes in all patients during the entire study period, by treatment arm

@@

## Table S3 Outcomes in all patients before training, by treatment arm

@@

## Table S4 Outcomes in all patients after training, by treatment arm

@@

## Table S5 Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Table S6 Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Table S7 Absolute and relative differences in outcomes after training, comparing standard care with ATLS

@@

## Table S8 Absolute and relative differences in outcomes after training, comparing standard care with PTC

@@

## Table S9 Absolute and relative differences in outcomes after training, comparing ATLS with PTC

@@

## Table S10 Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

@@

## Table S11 Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

@@

## Table S12 Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

>>>>

## Table S2. Outcomes in all patients during the entire study period, by treatment arm

@@

## Table S3. Outcomes in all patients before training, by treatment arm

@@

## Table S4. Outcomes in all patients after training, by treatment arm

@@

## Table S5. Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Table S6. Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Table S7. Absolute and relative differences in outcomes after training, comparing standard care with ATLS

@@

## Table S8. Absolute and relative differences in outcomes after training, comparing standard care with PTC

@@

## Table S9. Absolute and relative differences in outcomes after training, comparing ATLS with PTC

@@

## Table S10. Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

@@

## Table S11. Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

@@

## Table S12. Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC
